Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-11 Paper/RSVOptimization.rnw
Improved figure placement and legend layout

<<map, results='hide'>>=
    tikz(sprintf("%s/map.tex", figuresDir), width=inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
    US.counties = US.counties[US.counties$STATEFP == "09",]
    county.data = US.counties@data %>%
        mutate(id=rownames(.)) %>%
        data.table() %>%
        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))

@@

<<coverageByRegion, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            darkPurple, 
            NA, NA, 
            rep(c(darkBrown, darkOrange), each=3), darkPurple
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            16, 
            16, 16, 
            16, 15, 17, 
            16, 15, 17
          ), 
          drop=FALSE
        ) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
        scale_color_manual(
          name="Prophylaxis regimen", 
          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            darkPurple, darkPurple, 
            NA, NA, NA, NA, 
            rep(c(darkBrown, darkOrange), each=6)
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            16, 16, 
            16, 16, 16, 16, 
            16, 21, 15, 22, 17, 24, 
            16, 21, 15, 22, 17, 24
          ), 
          drop=FALSE
        ) + 
        scale_x_discrete(labels=roundingLabels) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat.isRepeat, group=strat.isRepeat), 
            width=.25, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
        labs(x="Calendrical rounding", y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        theme(
            legend.position="bottom"
        )
    dev.off()
@

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen. Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection. Hollow plot markers ($\Circle$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
\label{fig:coverageByRoundingRegimen}
\end{center}
\end{figure}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
          values=c(
            darkPurple, 
            NA, NA, 
            rep(c(darkBrown, darkGreen), each=3), darkPurple
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
          values=c(
            16, 
            16, 16, 
            16, 15, 17, 
            16, 15, 17
          ), 
          drop=FALSE
        ) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction") +
        guides(color=guide_legend(keywidth=3, keyheight=1, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

>>>>

<<map, results='hide'>>=
    tikz(sprintf("%s/map.tex", figuresDir), width=1.5*inlinePlotWidth, height=inlinePlotHeight, pointsize=10)
    US.counties = readOGR(dsn="../Maps/cb_2016_us_county_5m",layer="cb_2016_us_county_5m")
    US.counties = US.counties[US.counties$STATEFP == "09",]
    county.data = US.counties@data %>%
        mutate(id=rownames(.)) %>%
        data.table() %>%
        mutate(highRSV=ifelse(NAME %in% lowIncidenceCounties, FALSE, TRUE))

@@

<<coverageByRegion, results='hide', warning=FALSE>>=
    GeomErrorbar$draw_key = draw_key_vline_small

    tikz(sprintf("%s/coverageByRegionRegimen.tex", figuresDir), width=pagePlotWidth, height=pagePlotHeight * 1.5, pointsize=10)
    data = unprotectedByCounty %>% 
        filter(county %in% countiesForPlots, rounding==0, sliding==FALSE) %>%
        mutate(strat=factor(strat, levels=c(levels(strat)[1], "_1", "_2", levels(strat)[2:7])))

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            darkPurple, 
            NA, NA, 
            rep(c(darkBrown, darkOrange), each=3), darkPurple
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6]))),
          values=c(
            16, 
            16, 16, 
            16, 15, 17, 
            16, 15, 17
          ), 
          drop=FALSE
        ) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction", color="Prophylaxis regimen") +
        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.90, 1.00), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_alpha_manual(guide=FALSE, breaks=c(FALSE, TRUE), values=c(1, 0.5)) + 
        scale_color_manual(
          name="Prophylaxis regimen", 
          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
          values=c(
            darkPurple, darkPurple, 
            NA, NA, NA, NA, 
            rep(c(darkBrown, darkOrange), each=6)
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          breaks=factor(sprintf("%s.%s", levels(data$strat), FALSE), levels=strat.isRepeat.levels),
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:6])), trailing=0),
          values=c(
            16, 16, 
            16, 16, 16, 16, 
            16, 21, 15, 22, 17, 24, 
            16, 21, 15, 22, 17, 24
          ), 
          drop=FALSE
        ) + 
        scale_x_discrete(labels=roundingLabels) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=rounding, color=strat.isRepeat, group=strat.isRepeat), 
            width=.25, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=rounding, color=strat.isRepeat, shape=strat.isRepeat), position=position_dodge(.5), size=0.75, fill="white") +
        labs(x="Calendrical rounding", y="Preventable fraction") +
        theme(
            legend.position="bottom",
            legend.key=element_rect(fill="white"),
        ) +
        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3))
    dev.off()
@

\begin{figure}
\begin{center}
\input{\figuresDir/coverageByRoundingRegimen.tex}
\caption[The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance]{The effect of calendrical rounding of start and end of spatially adjusted RSV prophylaxis regimens on their performance, showing that longer rounding intervals diminish the benefits of alternative regimens over the AAP-recommended regimen. Preventable fraction: the fraction of all RSV hospitalizations occurring while the prophylaxis regimen offers protection. Hollow plot markers ($\raisebox{1pt}{\Circle}$, $\square$, and $\triangle$) denote a prophylaxis strategy which, as a result of rounding, is identical to another, and therefore does not provide additional insights.}
\label{fig:coverageByRoundingRegimen}
\end{center}
\end{figure}

@@

    ggplot(data) +
        theme_light(base_size=plotTextBaseSize) +
        scale_y_continuous(labels=latexPercent, limits=c(0.9, 1), breaks=seq(0, 1, by=.02), expand=c(0.05, 0)) +
        scale_color_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
          values=c(
            darkPurple, 
            NA, NA, 
            rep(c(darkBrown, darkGreen), each=3), darkPurple
          ), 
          drop=FALSE
        ) + 
        scale_shape_manual(
          name="Prophylaxis regimen", 
          labels=legendLabels(c(as.vector(stratLabels[10]), "_1", "_2", as.vector(stratLabels[1:3]), as.vector(stratLabels[7:9]))),
          values=c(
            16, 
            16, 16, 
            16, 15, 17, 
            16, 15, 17
          ), 
          drop=FALSE
        ) + 
        geom_errorbar(
            aes(ymin=frac.lower, ymax=frac.upper, x=county, color=strat, group=strat), 
            width=.3, 
            position=position_dodge(.5)
        ) + 
        geom_point(aes(y=frac.median, x=county, color=strat, shape=strat), position=position_dodge(.5), size=.75) +
        labs(y="Preventable fraction") +
        guides(color=guide_legend(keywidth=1, keyheight=1.5, ncol=3)) + 
        scale_x_discrete(labels=countyLabels) + 
        theme(
            axis.title.x=element_blank(),
            axis.ticks.x=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
